Errata

### 2025-04-07 tex/Manuscript-5.tex
Refactor code structure for improved readability and maintainability

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M5-Figure_3.png}
	\caption{PLFA profiling of microbial community structure. The a) total content of extracted fatty acids (in \si{nmol\,C\text{-}FA\,\gram^{-1}}), the content of markers associated with b) fungi (\si{nmol\,C\text{-}FA\,\gram^{-1}}) and c) bacteria (\si{nmol\,C\text{-}FA\,\gram^{-1}}) and the d) fungi:bacteria ratio and e) Gram+:Gram− ratio in a topsoil and subsoil. Green boxes represent the living root phase (rhizosphere) and brown the decaying root phase (detritusphere) together with corresponding controls in faded colors. Asterisks denote significant differences between rooted and control samples (\(.P < 0.1\), *\(P < 0.05\), **\(P < 0.01\), ***\(P < 0.001\)). Box plots indicate medians (line) and means (x), where the first (Q1) and third (Q3) quartile are represented by the lower, respectively upper bounds of the box. Error bars represent the data range, bounded to \(1.5 \times (\text{Q3}-\text{Q1})\); (\(n = 6\) independent replicates).}
	\label{fig:M5-F3}
\end{figure}

@@

In the studied dryland soil, roots induced a shift in soil aggregation in the rhizosphere, leading to an increased contribution of water-stable macroaggregates to the total mass and an increased allocation of C and N to macroaggregates in both topsoil and subsoil (Figure \ref{fig:M5-F1}c and Figure \ref{fig:M5-F4}d; Figure \ref{fig:figure_4a_label}). This root effect is consistent with the well-established consensus that plant roots drive the formation of coarser aggregate structures, for example via root-derived gluing agents or direct entanglement of soil particles \citep{Tisdall1982, Six2004, Angst2018, Gregory2022}.

>>>>

\begin{figure}[H] % Requires float package
  \centering
  \includegraphics[width=1\textwidth]{img/M5-Figure_3.png} % Requires graphicx
  \caption{PLFA profiling of microbial community structure. The a) total content of extracted fatty acids (in \si{nmol\,C\text{-}FA\,\gram^{-1}}), the content of markers associated with b) fungi (\si{nmol\,C\text{-}FA\,\gram^{-1}}) and c) bacteria (\si{nmol\,C\text{-}FA\,\gram^{-1}}) and the d) fungi:bacteria ratio and e) $\text{Gram}^{+}:\text{Gram}^{-}$ ratio in a topsoil and subsoil. Green boxes represent the living root phase (rhizosphere) and brown the decaying root phase (detritusphere) together with corresponding controls in faded colors. Asterisks denote significant differences between rooted and control samples (\textbullet\(P < 0.1\), *\(P < 0.05\), **\(P < 0.01\), ***\(P < 0.001\)). Box plots indicate medians (line) and means (x), where the first (Q1) and third (Q3) quartile are represented by the lower, respectively upper bounds of the box. Error bars represent the data range, bounded to \(1.5 \times (\text{Q3}-\text{Q1})\); (\(n = 6\) independent replicates).} % Requires siunitx, amsmath
  \label{fig:M5-F3} % Label placed after caption
\end{figure}

@@

In the studied dryland soil, roots induced a shift in soil aggregation in the rhizosphere, leading to an increased contribution of water-stable macroaggregates to the total mass and an increased allocation of C and N to macroaggregates in both topsoil and subsoil (Figure \ref{fig:M5-F1}c and Figure \ref{fig:M5-F4}d; Figure \ref{fig:M5-F4}a). This root effect is consistent with the well-established consensus that plant roots drive the formation of coarser aggregate structures, for example via root-derived gluing agents or direct entanglement of soil particles \citep{Tisdall1982, Six2004, Angst2018, Gregory2022}.
